Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-28 writeup/gz_hubble_data.tex
Fix last sig fig on WMAP9 parameters. Closes #162.

This paper assumes the WMAP9 cosmological parameters of
$(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.

@@

Images with simulated AGN were classified in the interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
usng the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim14} uses similarly-processed images for reliable
identification of bulgeless galaxies using SDSS data.

>>>>

This paper assumes the WMAP9 cosmological parameters of
$(\Omega_m,\Omega_\Lambda,h)=(0.286,0.714,0.693)$ \citep{hin13}.

@@

Images with simulated AGN were classified in the interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
usng the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.
